Robotic Cart System

### 2021-04-28 parts/20-system_architecture.tex
Update 20-system_architecture.tex

\vspace*{12pt}
\noindent
The Mobile Cart subsystem block diagram, shown in Fig. \ref{fig:mobile_block_diag}, is the most complex of the two subsystems. The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue). The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart. The final input to the mobile cart subsystem is the incoming RF signals. These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer which takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer. Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.

>>>>

\vspace*{12pt}
\noindent
The Mobile Cart subsystem block diagram, shown in Fig. \ref{fig:mobile_block_diag}, is the most complex of the two subsystems. The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue). The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart. The final input to the mobile cart subsystem is the incoming RF signals. These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer. The dual-direction multiplexer then takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer. Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.
